---
title: "Daily Schedule"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

<button class="accordion">Before Starting the Program</button>
<div class="panel"> 

| Topic                              | Links |
|------------------------------------|-------|
| Download and Install R | [Link](https://mirror.las.iastate.edu/CRAN/)|
| Download and Install RStudio| [Link](https://www.rstudio.com/products/rstudio/download/)|
|Download packages |<a href="R-code/code-00-setup.R" download>File</a>|
|Alzheimer's Disease | [Link](https://www.youtube.com/watch?v=LrcL3vJjN2g) |

</div>




<button class="accordion">Day 1 &#9679; Data Science -- Basics and Principles  </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 9:00 - 9:15 | Welcome                            |[Slides](https://uci-data-academy.github.io/slides/01a-welcome.html)|
| 9:15 - 9:45 | Introduction to data science    |[Slides](https://uci-data-academy.github.io/slides/01b-intro-data-science.html)|
| 10:00 - 10:45 | Describing data    |[Slides](https://uci-data-academy.github.io/slides/01c-describe-data.html)   |
| 11:00 - 12:00 | Introduction to the capstone project |                [Slides](https://uci-data-academy.github.io/slides/2023_Intro_to_AD_Online.pdf)    |
| 1:30 - 2:30 | Introduction to R |[Slides](https://uci-data-academy.github.io/slides/Lab-01a-intro-r-schetzsle.html) |
| 2:45 - 3:30 | R packages |[Slides](https://uci-data-academy.github.io/slides/Lab-01b-R-packages.html) |
</div>
		




<button class="accordion">Day 2 &#9679; Probability and estimation </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 9:00 - 9:45 | Introduction to probability |[Slides](https://uci-data-academy.github.io/slides/02a-intro-prob.html) |
| 10:00 - 10:45 | Estimation |[Slides](https://uci-data-academy.github.io/slides/02b-estimation.html)       |
| 11:00 - 11:45 | Importing data              |[Slides](https://uci-data-academy.github.io/slides/Lab-01c-import-data-schetzsle.html)  |
|1:30 - 2:15 | R Markdown             |[Slides](https://uci-data-academy.github.io/slides/Lab-02a-intro-rmarkdown-moslemi.html)  |
| 2:30 - 3:30 | Tidyverse              | [Slides](https://uci-data-academy.github.io/slides/Lab-01d-intro-tidyverse-moslemi.html)     |

</div>
	
	

	



<button class="accordion">Day 3 &#9679; Hypothesis testing and examining Relationships </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 9:00 - 10:00 | Hypothesis testing |[Slides](https://uci-data-academy.github.io/slides/03a-hypothesis.html)|
| 10:15 - 11:00 | Exploring and examining relationships  |[Slides](https://uci-data-academy.github.io/slides/03b-relationship.html)|
| 11:15 - 12:00 | Data wrangling |[Slides](https://uci-data-academy.github.io/slides/Lab-02b-data-wrangling.html) [Scratchwork](https://uci-data-academy.github.io/slides/TA_scratchwork/data_wrangling_scratchwork.R) |
| 2:30 - 3:30 | Data visualization in R |[Slides](https://uci-data-academy.github.io/slides/Lab-02b-visualize-data-schetzsle.html)     |
| 2:30 - 3:00 | Commonly used R functions |[Slides](https://uci-data-academy.github.io/slides/TA_scratchwork/Commonly_Used_R_Functions.html) |

</div>
		
	




<button class="accordion">Day 4 &#9679; Linear regression </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 9:00 - 10:45 | Introduction to linear regression                        |[Slides](https://uci-data-academy.github.io/slides/04a-regression.html) |
| 11:00 - 11:45 | Linear regression in R              |[Slides](https://uci-data-academy.github.io/slides/Lab-07-Linear_regression.html) |
| 1:30 - 2:15 | Data visualization with the Alzhiemer's dataset |[Slides](https://uci-data-academy.github.io/slides/Lab-06-exploring-AD-data.html) [Scratchwork](https://uci-data-academy.github.io/slides/TA_scratchwork/Data_visualization.R)      |
| 2:30 - 3:30 | Linear regression examples from capstone              |[Slides](https://uci-data-academy.github.io/slides/Lab-07-Linear_regression_AD.html) [Scratchwork](https://uci-data-academy.github.io/slides/TA_scratchwork/Linear_regression_AD.R)|
</div>
		
	


<button class="accordion">Day 5 &#9679; Logistic regression </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 9:00 - 10:45 | Introduction to logistic regression |[Slides](https://uci-data-academy.github.io/slides/05a-logit.html)|
| 11:00 - 11:45 | Logistic regression examples from capstone | [Slides 1](https://uci-data-academy.github.io/slides/Lab-08-Logistic_regression_AD.html) [Slides 2](https://uci-data-academy.github.io/slides/Lab-08-Data-Splitting-and-Prediction.html) [Scratchwork](https://uci-data-academy.github.io/slides/TA_scratchwork/Logistic_regression_AD.R) |
| 1:30 - 2:15 | Starting capstone projects | |
</div>
			
	
			

<button class="accordion">Day 6-10 &#9679; Capstone Project </button>
<div class="panel">

Lasso Regression examples from AD dataset [Slides](https://uci-data-academy.github.io/slides/Lab-09-Lasso-Regression.html)
</div>



<button class="accordion">Day 11 &#9679; Machine Learning -- Intro and K Nearest Neighbors   </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
|9:00 - 9:45 | Introduction to Machine Learning | [Slides](https://uci-data-academy.github.io/slides/Machine_Learning_Slides/01-Introduction.pdf) [Handout](https://uci-data-academy.github.io/slides/Machine_Learning_Handouts/01-Intro.pdf) |
|10:00 - 11:45 | K Nearest Neighbors Algorithm | [Slides](https://uci-data-academy.github.io/slides/Machine_Learning_Slides/02-NearestNeighborClassifiers.pdf) [Handout](https://uci-data-academy.github.io/slides/Machine_Learning_Handouts/02-NearestNeighbors.pdf)
| 1:30 - 3:30 | K Nearest Neighbors Lab with Alzheimer's Data |[Slides](https://uci-data-academy.github.io/slides/Lab-10-KNN.html) [Scratchwork](https://uci-data-academy.github.io/slides/TA_scratchwork/KNN.R)|
</div>



<button class="accordion">Day 12 &#9679; Concept Learning   </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
|9:00 - 11:45 | Concept Learning | [Handout](https://uci-data-academy.github.io/slides/Machine_Learning_Handouts/03-ConceptLearning.pdf) |
|1:30 - 3:45 | Concept Learning with Alzheimer's Data | |
	
	
	
	
	
```{r}
htmltools::tagList(
  htmltools::tags$script(src = "https://d3js.org/d3.v4.min.js"),
  htmltools::tags$script(src = "https://cdnjs.cloudflare.com/ajax/libs/dimple/2.3.0/dimple.latest.min.js")
)
```

```{js, class.source = "jsvis1"}
var acc = document.getElementsByClassName("accordion");
var i;

for (i = 0; i < acc.length; i++) {
  acc[i].addEventListener("click", function() {
    /* Toggle between adding and removing the "active" class,
    to highlight the button that controls the panel */
    this.classList.toggle("active");

    /* Toggle between hiding and showing the active panel */
    var panel = this.nextElementSibling;
    if (panel.style.display === "block") {
      panel.style.display = "none";
    } else {
      panel.style.display = "block";
    }
  });
}
```
