---
title: "Daily Schedule"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

<button class="accordion">Before Starting the Program</button>
<div class="panel"> 

| Topic                              | Links |
|------------------------------------|-------|
| Download and Install R | [Link](https://mirror.las.iastate.edu/CRAN/)|
| Download and Install RStudio| [Link](https://www.rstudio.com/products/rstudio/download/)|
|Download packages |<a href="R-code/code-00-setup.R" download>File</a>|
|Alzheimer's Disease | [Link](https://www.youtube.com/watch?v=LrcL3vJjN2g) |

</div>




<button class="accordion">Day 1 &#9679; Data Science -- Basics and Principles  </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 9:00 - 9:30 | Welcome                            |[Slides](https://uci-data-academy.github.io/slides/01a-welcome.html)|
| 9:35 - 10:30 | Introduction to data science    |[Slides](https://uci-data-academy.github.io/slides/01b-intro-data-science.html)|
| 10:45 - 12:00 | Describing data    |[Slides](https://uci-data-academy.github.io/slides/01c-describe-data.html)   |
| 2:00 - 2:45 | Introduction to the capstone project |                [Slides](https://uci-data-academy.github.io/slides/01d-intro-capstone-project.pdf)    |
| 3:00 - 4:00 | Introduction to R                            |[Slides](https://uci-data-academy.github.io/slides/Lab-01a-intro-r-schetzsle.html) |

</div>
		




<button class="accordion">Day 2 &#9679; Lab: Introduction to R </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 9:00 - 10:00 | R programming  | |
| 10:15 - 10:45 | R packages |[Slides](https://uci-data-academy.github.io/slides/Lab-01b-R-packages-schetzsle.html)       |
| 10:45 - 12:00 | Importing data               |[Slides](https://uci-data-academy.github.io/slides/Lab-01c-import-data-schetzsle.html)  |
| 1:00 - 1:45 | Tidyverse              | [Slides](https://uci-data-academy.github.io/slides/Lab-01d-intro-tidyverse-moslemi.html)     |
| 2:00 - 3:00 | Data wrangling              | [Slides](https://uci-data-academy.github.io/slides/Lab-01e-data-wrangling-moslemi.html)     |

</div>
	
	

	



<button class="accordion">Day 3 &#9679; Probability and Inference </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 9:00 - 10:00 | Introduction to probability |[Slides](https://uci-data-academy.github.io/slides/02a-intro-prob.html)|
| 10:15 - 11:00 | Estimating  |[Slides](https://uci-data-academy.github.io/slides/02b-estimation.html)|
| 11:15 - 12:00 | Hypothesis testing |[Slides](https://uci-data-academy.github.io/slides/02c-hypothesis.html)|
| 2:00 - 3:00 | Probability through simulations| [Slides](https://uci-data-academy.github.io/slides/02d-intro-prob-simulation.pdf) [File](https://uci-data-academy.github.io/slides/02d-intro-prob-simulation-code.R)|
| 3:15 - 4:00 | Inference examples from the capstone project| [Slides](https://uci-data-academy.github.io/slides/02e-capstone-estimation.pdf) [File](https://uci-data-academy.github.io/slides/02e-capstone-estimation-code.R)|

</div>
		
	




<button class="accordion">Day 4 &#9679; Lab: Advanced R </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 9:00 - 10:15 | R Markdown                        |[Slides](https://uci-data-academy.github.io/slides/Lab-02a-intro-rmarkdown-moslemi.html) |
| 10:45 - 12:00 | Practicing R Markdown            | |
| 1:00 - 2:00 | Data visualization in R |[Slides](https://uci-data-academy.github.io/slides/Lab-02b-visualize-data-schetzsle.html)       |
| 2:15 - 3:00 | Practicing data visualization              | 
|

</div>
		
	


<button class="accordion">Day 5 &#9679; Statistical Modeling </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 9:00 - 10:15 | Exploring and examining relationships |[Slides](https://uci-data-academy.github.io/slides/03a-relationship.html)|
| 10:30 - 12:00 | Linear regression |[Slides](https://uci-data-academy.github.io/slides/03b-regression.html)|
| 1:30 - 2:15 | Logistic regression |[Slides](https://uci-data-academy.github.io/slides/03c-logit.html)|
| 2:30 - 3:00 | Relationship examples from the capstone project |[Slides](https://uci-data-academy.github.io/slides/03d-capstone-relationship.pdf) [File](https://uci-data-academy.github.io/slides/03d-capstone-relationship-code.R)|
| 3:15 - 4:00 | Regression examples from the capstone project| [Slides](https://uci-data-academy.github.io/slides/03e-capstone-regression.pdf) [File](https://uci-data-academy.github.io/slides/03e-capstone-regression-code.R)|
</div>
			
	
			

<button class="accordion">Day 6-10 &#9679; Capstone Project </button>

	
	
	
	
	
```{r}
htmltools::tagList(
  htmltools::tags$script(src = "https://d3js.org/d3.v4.min.js"),
  htmltools::tags$script(src = "https://cdnjs.cloudflare.com/ajax/libs/dimple/2.3.0/dimple.latest.min.js")
)
```

```{js, class.source = "jsvis1"}
var acc = document.getElementsByClassName("accordion");
var i;

for (i = 0; i < acc.length; i++) {
  acc[i].addEventListener("click", function() {
    /* Toggle between adding and removing the "active" class,
    to highlight the button that controls the panel */
    this.classList.toggle("active");

    /* Toggle between hiding and showing the active panel */
    var panel = this.nextElementSibling;
    if (panel.style.display === "block") {
      panel.style.display = "none";
    } else {
      panel.style.display = "block";
    }
  });
}
```
